Subsegmental language detection in Celtic language text

### 2014-06-27 codeswitch-cltw-2014/codeswitch_camera_ready.tex
bib
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55037 72bbbca6-d526-0410-a7d9-f06f51895060
+
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55041 72bbbca6-d526-0410-a7d9-f06f51895060

Apart from the techniques discussed in section~\ref{sec:method}, some baselines are also used to give a comparative view of how well all the mechanism perform.

@@

% include your own bib file like this:
\bibliographystyle{acl}
\bibliography{codeswitch}

>>>>

Apart from the techniques discussed in section~\ref{sec:method}, some baselines are also used to give a comparative view of how well all the mechanisms perform.

@@

% include your own bib file like this:
\bibliographystyle{acl}
\bibliography{codeswitch_camera_ready}
